Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
spatial p

Social interactions exists across both temporal and spatial scales [@Whitehead_2008]. For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social associations
over long time periods 
represent shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Individuals must share space to 
interact or associate and thus have overlapping
home ranges [@Vander_2014]. Home
range overlap is an example of how animals share space over coarser spatial and
temporal scales <!-- TODO to create their social environment -->[e.g. @Piza_Roca_2018]. Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of social interactions, such as social association and home range overlap, vary
predictably [@Castles_2014; @Farine_2015a]. 
We therefore define social scale as the explicit definition 
and measurement of social relationships [@Farine_2015a]. 
<!-- for QW:

-->
<!-- and suggest the potential for adaptive variance in social relationships is also scale-dependent.  -->
<!--QW: also need to fix up this last sentence- I added the 'adaptive variance part 
under the expectation that there is some scale at which variance is greatest, and presumably
it is this scale that has the greatest effect on fitness or other traits-->

@@

# Results
Individuals in multilayer networks became more connected as the social distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in foraging and open layers, and lower
strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased sharply between 5 m and 100 m in all three habitat classes followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength decreased. 
GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] us to
confirm the use of 50 m buffer that has long been used for studies in the field
[@Lingle_2003; @Clutton_1982]

@@

<!-- spatial -->
Habitat selection, the use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009].

Social structure and habitat selection are intimately related: individuals must
share space to interact and the distribution of resources influences group
dynamics and home range size [@Webber_2018]. Social structure is influenced by
resource availability and seasonality [@Peignier_2019], configuration [@He_2019]
and fragmentation [@Banks_2007].  Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, the (3) habitat patches within the home range and
(4) specific resources within a habitat patch. Kie et al. [-@Kie_2002] found
that, independently, third order of selection was insufficient for capturing
landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
scale larger than their home range size. Moving past this hierarchical
perspective, Mayor (2007) emphasized the importance of considering a broad
continuum of scales to reveal scale-dependent selection and avoid the bias of
predefined scales assumed to be associated with certain behaviours.

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015]. Caribou
social network graph strength was higher in winter and contrastingly lower in
summer when resource availability is more homogeneous [@Peignier_2019]. Bison
(*Bison bison*) showed stronger habitat selection in larger groups, and
avoidance of predation risk was a main factor contributing to their habitat
selection [@Fortin_2009]. These examples, comparing sociality and habitat
selection across spatial and temporal contexts, are implicitly multilayer
analyses.

@@

>>>>

Social interactions exists across both temporal and spatial scales [@Whitehead_2008]. For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social associations
over long time periods 
represent shared space use by members of the same social group [Figure
\@ref(fig:spacetime), @Franks_2009]. Individuals must share space to 
interact or associate and thus have overlapping
home ranges [@Vander_2014]. Home
range overlap is an example of how animals share space over coarser spatial and
temporal scales <!-- TODO to create their social environment -->[e.g. @Piza_Roca_2018]. Although the social environment
clearly scales spatially and temporally, it remains unclear whether coarser
scales of social interactions, such as social association and home range overlap, vary
predictably [@Castles_2014; @Farine_2015a]. 
We therefore define social scale as the explicit definition 
and measurement of social relationships [@Farine_2015a]. 
<!-- for QW:  -->
<!-- and suggest the potential for adaptive variance in social relationships is also scale-dependent.  -->
<!--QW: also need to fix up this last sentence- I added the 'adaptive variance part 
under the expectation that there is some scale at which variance is greatest, and presumably
it is this scale that has the greatest effect on fitness or other traits-->

@@

# Results
<!-- TODO intro + ml fig -->

Individuals in multilayer networks became more connected as the social distance
threshold increased. Mean graph strength differed across habitat layers with
similar and higher graph strength in foraging and open layers, and lower
strength in forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased sharply between 5 m and 100 m in all three habitat classes followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength decreased. 
GPS data allows [e.g. from this study and @Peignier_2019; @Lesmerises_2018] us to
confirm the use of 50 m buffer that has long been used for studies in the field
[@Lingle_2003; @Clutton_1982]

@@

<!-- spatial -->
Habitat selection, the use of
available resources or landscape features by animals [@Manly_1993; @Boyce_1999],
is a scale-dependent process [@Mayor_2009]. Social structure and 
habitat selection are intimately related and individuals must
share space to interact [@Webber_2018]. Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, the (3) habitat patches within the home range and
(4) specific resources within a habitat patch. Kie et al. [-@Kie_2002] found
that, independently, third order of selection was insufficient for capturing
landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
scale larger than their home range size. Scales of habitat selection could be 
relevant for multilayer networks and our integration of habitat within a 
multilayer context could be an important first step (see Figure \@ref(fig:lcres)). 
Specifically, if individuals select habitats at the 
home range scale, it may be relevant to assess social structure at 
the home range overlap scale in a multilayer framework. By contrast,
in cases where individuals select habitats at the patch-scale, 
more fine-scale measures of sociality may be relevant. Moving past this hierarchical
perspective, Mayor (2007) emphasized the importance of considering a broad
continuum of scales to reveal scale-dependent selection and avoid the bias of
predefined scales assumed to be associated with certain behaviours.

<!-- TODO: missing results -->

<!-- spatial -->

<!-- temp -->
The emergent relationship between habitat and sociality has been explored by the
temporal distribution and phenology of resources and use of social information. 
<!-- TODO: results -->

For
example, cougar (*Puma concolor*) home ranges overlapped more in regions with
high hunting opportunity, a proxy for resource richness [@Elbroch_2015].

Bison
(*Bison bison*) showed stronger habitat selection in larger groups, and
avoidance of predation risk was a main factor contributing to their habitat
selection [@Fortin_2009]. These examples, comparing sociality and habitat
selection across spatial and temporal contexts, are implicitly multilayer
analyses.

@@

<!-- TODO repeat qs-->
